Wind_analyses

### 2019-03-08 Wind_analyses.Rmd
updated

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  dplyr::rename(site = temp_sites) %>% 
  select(site, date, hour, dir, speed)
```

Things to do*******

- Match temp and wind data
- Create plots shwoing predominant wind direction during an upwelling evnt

>>>>

wind_data <- rbind(wind_3_HoutBay,wind_sitesmatched_3,wind_sitesmatched_2,wind_sitesmatched_1)
wind_data <- wind_data %>% 
  dplyr::rename(site = temp_sites) %>% 
  mutate(date = as.Date(date)) %>% 
  mutate(hour = as.numeric(hour),
         dir = as.numeric(dir),
         speed = as.numeric(speed)) %>% 
  select(site, date, hour, dir, speed)

# save(wind_data, file = "Data/wind_data.RData")

# The wind data

wind_daily <- wind_data %>%
  mutate(date = as.Date(date)) %>%
  group_by(site, date) %>%
  summarise(dir_circ = mean.circular(circular(dir, units = "degrees")),
            speed_circ = mean.circular(circular(speed, units = "degrees")))
# save(wind_daily, file = "Data/wind_daily.RData")

load("Data/wind_daily.RData") # Loading the daily wind data for each of the sites
```

## Matching remotely sensed SST's with the wind data

Loading the SST datasets: 
```{r}

## Load in the sea surface temperatue datasets
## See the Dectect_MCS.Rmd script for more info. The datasets loaded here are only for temperatures collected between the years 1992-2016. However if a longer time series is required changes may  be made to the Dectect_MCS.Rmd script (line 136)

load("Data/overlap_ts.RData")
load("Data/insitu_MUR.RData")
load("Data/insitu_OISST.RData")
load("Data/insitu_G1SST.RData")
load("Data/insitu_K10.RData")

# Select only the years 2014 and 2015
filtered_years <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2014, 2015)) %>% 
  drop_na()
}

SACTN_fyears <- filtered_years(df = overlap_ts) 
MUR_fyears <- filtered_years(df = insitu_MUR) 
OISST_fyears <- filtered_years(df = insitu_OISST) 
G1SST_fyears <- filtered_years(df = insitu_G1SST) 
K10_fyears <- filtered_years(df = insitu_K10)

# save(SACTN_fyears, file = "Data/temp_2014_2015/SACTN_fyears.RData")
# save(MUR_fyears, file = "Data/temp_2014_2015/MUR_fyears.RData")
# save(OISST_fyears, file = "Data/temp_2014_2015/OISST_fyears.RData")
# save(G1SST_fyears, file = "Data/temp_2014_2015/G1SST_fyears.RData")
# save(K10_fyears, file = "Data/temp_2014_2015/K10_fyears.RData")

temp_wind <- function(df){
  combined <- df %>% 
  left_join(wind_daily, by = c("site", "date")) %>% 
  #select(-combi) %>% 
  na.trim()
  return(combined)
}

temp_wind_MUR <- temp_wind(df = MUR_fyears)
temp_wind_SACTN <- temp_chloro(df = SACTN_fyears)
temp_wind_OISST <- temp_chloro(df = OISST_fyears)
temp_wind_G1SST <- temp_chloro(df = G1SST_fyears)
temp_wind_K10 <- temp_chloro(df = K10_fyears)
```

- Create plots shwoing predominant wind direction during an upwelling evnt
- Create wavelet analyses
